Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
fix anglais

The $\sigma$ function takes as parameters the index of the starting abstract
value, and the path we focus on. If we dynamically construct this function
during the analysis, we should store the results of the sigma function into a
compact representation, such as Algebraic Decision Diagrams. Notice that the
image of a couple $(j,k)$ by the function $\sigma$ will be computed only if
needed.

>>>>

The $\sigma$ function takes as parameters the index of the starting abstract
value, and the path we focus on. If we dynamically construct this function
during the analysis, we should store the results of the $\sigma$ function into a
compact representation, such as Algebraic Decision Diagrams.
\DM{Pourquoi des ADD et pas des BDD?}
Note that $\sigma(j,k)$ will be computed only if needed.
